### 2023-12-05 main.tex
l
ll

\todo{but these are the correlations, no?}

@@

	\item In Section~\ref{correlation-section} we show, using duality, that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$. By exploiting a binomial formula we rewrite the correlations in terms
	as a polynomial in the left and right boundary densities with coefficients given by the absorption probabilities, as claimed in Corollary~\ref{Corolollary-ABS_Corr-abstract}.

@@

@@

Consider the matrices
	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen}\co\\
	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\dt\label{S2Gen}
We introduce

@@

We introduce
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
whichdenotes $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.

>>>>

@@

	\item In Section~\ref{correlation-section} we show that the correlations are in turn the components of the vector $|\Psi^{'}\rangle$. 
	By exploiting a binomial formula we rewrite the correlations in terms
of polynomials in the left and right boundary densities with coefficients given by the absorption probabilities, as claimed in Corollary~\ref{Corolollary-ABS_Corr-abstract}.

@@

	\todo{to discuss}

@@

Consider the matrix
	\mathcal{S}_{1}:=\exp{\left(\sum_{a=1}^{N-1}e_{Na}\right)}\label{S1Gen}\co

@@

We introduce
\begin{align} 
	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}\right)}\dt\label{S2Gen}
\end{align}
and
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
which denotes $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$. By taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{\text{left}}^{''}+H_{\text{bulk}}+H_{\text{right}}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{\text{left}}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{\text{right}}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
